\documentclass[jou]{apa6}

\usepackage[american]{babel}

\usepackage{csquotes}
\usepackage[style=apa,sortcites=true,sorting=nyt,backend=biber]{biblatex}
\DeclareLanguageMapping{american}{american-apa}
\addbibresource{bibliography.bib}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Discrete Structures
%% The start of RBS stuff
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Working internal and external links in PDF
\usepackage{hyperref}
% Extra math symbols in LaTeX
\usepackage{amsmath}
\usepackage{gensymb}
\usepackage{amssymb}
% Enumerations with (a), (b), etc.
\usepackage{enumerate}
\usepackage[framemethod=TikZ]{mdframed}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage[justification=centering]{caption}
\usepackage{fancyvrb}
%\usepackage{changepage}
\usepackage{caption}% http://ctan.org/pkg/caption
\captionsetup[table]{format=plain,labelformat=simple,labelsep=period}%

\def\changemargin#1#2{\list{}{\rightmargin#2\leftmargin#1}\item[]}
\let\endchangemargin=\endlist 


\let\OLDitemize\itemize
\renewcommand\itemize{\OLDitemize\addtolength{\itemsep}{-6pt}}

\usepackage{etoolbox}
\makeatletter
\preto{\@verbatim}{\topsep=3pt \partopsep=3pt }
\makeatother

% These sizes redefine APA for A4 paper size
\oddsidemargin 0.0in
\evensidemargin 0.0in
\textwidth 6.27in
\headheight 1.0in
%\topmargin -24pt
\topmargin -32pt
\headheight 12pt
\headsep 12pt
%\textheight 9.19in
\textheight 9.35in


\title{Sample Quiz 8}
\author{Discrete Structures, Spring 2020}
\affiliation{RBS}

\leftheader{Discrete Sample Quiz 8}

\abstract{%
}

%\keywords{}

\setlength\parindent{0pt}

\begin{document}

\twocolumn
\thispagestyle{empty}

\begin{center}
{\Large Alternative Homework 3:}\\
{\Large Linear Optimization}
\end{center}

\begin{changemargin}{10pt}{10pt}
{\footnotesize
{\em Note.} This is a parody of MIT OCW content.\\
See \url{https://ocw.mit.edu/terms/}. 
The original assignments and related materials can be retrieved from 
\url{https://bit.ly/2YcyvII}, \url{https://bit.ly/30R4j7S} and 
\url{https://bit.ly/2YcgCtW}.
}
\end{changemargin}


%% (Only Simplex algorithm; the course focuses on "Advanced algorithms" in general)
%% Added to the simplex chapter (5.2)
%% https://ocw.mit.edu/courses/electrical-engineering-and-computer-science/6-046j-design-and-analysis-of-algorithms-spring-2015/assignments/MIT6_046JS15_pset8.pdf
% https://ocw.mit.edu/courses/electrical-engineering-and-computer-science/6-046j-design-and-analysis-of-algorithms-spring-2015/index.htm





%% Newest LP Course
%% https://ocw.mit.edu/courses/electrical-engineering-and-computer-science/6-854j-advanced-algorithms-fall-2008/
%% HW3 (P4: Scooter problem)
%% https://ocw.mit.edu/courses/electrical-engineering-and-computer-science/6-854j-advanced-algorithms-fall-2008/assignments/ps3.pdf
%% (Added to the simplex chapter 5.1, 5.2, 5.3, 5.4)

\vspace{4pt}
{\bf Question 1.} A warehouse has to ship 480 boxes of apples, 400 boxes of pears and 230 boxes
of quinces every day. 
It can ship any product by mail, by courier or by drone. 
The couriers can ship up to 420 boxes of any product; drones can ship up to 250 boxes. Regular mail can ship any number of boxes. 
Each shipment method has different costs, different speed (and therefore \textendash{} different earnings). 
The money earned by the warehouse per every box (depending on the product and its shipment method) is shown in the table:

\vspace{4pt}
\begin{tabular}{|l|c|c|c|} \hline
Product & Mail & Courier & Drone \\ \hline
Apples & $4$ EUR & $12$ EUR & $7$ EUR \\ \hline
Pears & $4$ EUR & $13$ EUR & $9$ EUR \\ \hline
Quinces & $8$ EUR & $14$ EUR & $11$ EUR \\ \hline
\end{tabular}

\vspace{4pt}
{\bf (A)} Write a Linear Program in a form that is 
an appropriate starting point for a simplex method.\\
{\bf (B)} Write all the steps for the simplex method with Dantzig pivot rule, which is the most common one. (Pivot rules 
can be found e.g.\ here: \url{https://bit.ly/3fDMzkn}).\\
{\bf (C)} Find the actual number of boxes to ship by each method to maximize the money earned.
Are the answers obtained from the simplex  method integer numbers?


%% Combinatorial Optimization stuff - in 5.1, 5.2, 5.3, 5.4
%% https://ocw.mit.edu/courses/mathematics/18-433-combinatorial-optimization-fall-2003/assignments/a3.pdf
%% https://www.chegg.com/homework-help/questions-and-answers/problem-4-meat-packing-plant-produces-480-hams-400-pork-bellies-230-picnic-hams-every-day--q19404846


\vspace{10pt}
{\bf Question 2.} A team of $n$ members would like to travel a distance $d$ from $A$ to $B$
as quickly as possible. All of them can walk and they also have one scooter \textendash{} initially 
the scooter is located in the point $A$ and can be used to carry only one person at a time.  
For each person $i$ ($1 \leq i \leq n$), we
know his/her walking speed $w_i$ and his/her speed $s_i$ when travelling on the scooter.
The goal is to find a way to bring all $n$ people to destination so as to minimize the
time at which the last person arrives. The scooter can be left by any member of the
group on the side of the road, and picked up by anyone else of the group. Members
of the group can also walk or use the scooter backwards (towards $A$) if that helps.

\vspace{4pt}
{\bf (A)} Consider the case where $n = 3$, $w_1 = w_2 = 1$, $s_1 = s_2 = 6$, $w_3 = 2$, $s_3 = 8$ and
$d = 100$. Find the fastest way for everyone to travel the distance $d$.\\
{\bf (B)} For a general instance (general $n$ and arbitrary speeds), write a linear program
whose value is always a lower bound on the time needed for the $n$-person team
to travel a distance $d$. This should be a small linear program; the number
of variables and constraints should be $O(n)$ (and not dependent on $d$, or the
number of `legs' of the solution).\\
{\bf (C)} Write a different variant of the linear program, if nobody is allowed 
to walk or to use the scooter in the backwards direction (towards $A$). 
Can this restriction increase the total travel time?

(This is a parody of Problem 4, see \url{https://bit.ly/3ectpC2}.)


%% Older LP Course
%% https://ocw.mit.edu/courses/electrical-engineering-and-computer-science/6-854j-advanced-algorithms-fall-2005/
%% HW6 (P3: Polytope and ball problem; P4: Students and Desks problem)
%% https://ocw.mit.edu/courses/electrical-engineering-and-computer-science/6-854j-advanced-algorithms-fall-2005/assignments/ps6.pdf


%\vspace{10pt}
%{\bf Question 3.} 
%You are given a bounded polytope in an $n$-dimensional space $\mathbb{R}^n$ 
%defined by a collection of inequalities $A\mathbf{x} \leq \mathbf{b}$ (where $A$ is an $m \times n$ matrix, $\mathbf{x} \in \mathbb{R}^n$ 
%and $\mathbf{b} \in \mathbb{R}^m$), and
%want to determine the smallest ball that contains the polytope. Show how to write 
%a linear program to identify the center of that ball.
%{\em Note.} A polytope is called bounded, if there exists a positive number $r > 0$ such that 
%all the feasible vectors $\mathbf{x} \in \mathbb{R}^n$ satisfying a
%system of $m$ inequalities $A\mathbf{x} \leq \mathbf{b}$ fall within a large sphere with radius $r$, 
%i.e. $|\mathbf{x}| \leq r$; i.e. the ``polytope'' is not infinite/unbounded.
% (This is a parody of Problem 3, see \url{https://bit.ly/2YHSD4N}.)

\vspace{10pt}
{\bf Question 3.} 
% yy <- round(2*(xx + rnorm(5)))
You are given the following points in the plane:
$$(1, 3), (2, 5), (3, 6), (5, 8), (8, 13).$$
We denote them by $(x_1,y_1)$, $\ldots$, $(x_5,y_5)$ respectively.\\
{\bf (A)} Find a line $ax + by = c$ that approximately passes through these points (no line is a
perfect fit). Write a linear program (you don't need to solve it) to find the line that minimizes the
maximum absolute error:
$$\max_{i \in \{1,\ldots,5\}} |ax_i + by_i - c|.$$
{\bf (B)} Is there a linear program that minimizes the total quadratic error? It is expressed like this:
$$\sum\limits_{i \in \{1,\ldots,5\}} (ax_i + by_i - c)^2.$$

(This is a parody of Problem 7.8, see p.240 \url{https://bit.ly/2YcgCtW}.)




%% Even older LP Course
%% https://ocw.mit.edu/courses/mathematics/18-433-combinatorial-optimization-fall-2003/index.htm


%% Oldest LP Course
%% https://dspace.mit.edu/bitstream/handle/1721.1/36897/6-854JFall-1999/OcwWeb/Electrical-Engineering-and-Computer-Science/6-854JAdvanced-AlgorithmsFall1999/LectureNotes/index.htm
%% HW7 (P5: Currency converting to Yen)
%% https://dspace.mit.edu/bitstream/handle/1721.1/36897/6-854JFall-1999/NR/rdonlyres/Electrical-Engineering-and-Computer-Science/6-854JAdvanced-AlgorithmsFall1999/2C7C47C7-7F02-4BF9-A7E0-8A629555245B/0/ps7.pdf
%% H8 (P1: Intersection of two polyhedra)
%% https://dspace.mit.edu/bitstream/handle/1721.1/36897/6-854JFall-1999/NR/rdonlyres/Electrical-Engineering-and-Computer-Science/6-854JAdvanced-AlgorithmsFall1999/8F211420-7108-4779-8774-629FC5C263BD/0/ps8.pdf











\end{document}

