\documentclass[jou]{apa6}
%\documentclass[11pt]{article}
\usepackage{ucs}
\usepackage[utf8x]{inputenc}
\usepackage{changepage}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{gensymb}
\usepackage{amssymb}
\usepackage{enumerate}
\usepackage{tabularx}
\usepackage{lipsum}
\usepackage{hyperref}

\oddsidemargin 0.0in
\evensidemargin 0.0in
\textwidth 6.27in
\headheight 1.0in
\topmargin -0.1in
\headheight 0.0in
\headsep 0.0in
\textheight 9.0in

\usepackage{xcolor}

\setlength\parindent{0pt}

\newenvironment{myenv}{\begin{adjustwidth}{0.4in}{0.4in}}{\end{adjustwidth}}
\renewcommand{\abstractname}{Anotācija}
\renewcommand\refname{Atsauces}



\newcounter{alphnum}
\newenvironment{alphlist}{\begin{list}{(\Alph{alphnum})}{\usecounter{alphnum}\setlength{\leftmargin}{2.5em}} \rm}{\end{list}}


%16.3-6

\makeatletter
\let\saved@bibitem\@bibitem
\makeatother

\usepackage{bibentry}
%\usepackage{hyperref}


\title{Homework 1: Grading Criteria}
\author{Kalvis}
\affiliation{RBS}



\begin{document}
\thispagestyle{empty}

\twocolumn

\begin{center}
{\Large RBS: Discrete Structures}\\
{\Large Individual Presentations: Grading Guidelines}
\end{center}

You have all submitted your draft slide decks - each about your individual topic. Thank you for your good work. 
These presentations are worth 10\% of your grade. The criteria to evaluate your presentation are the following: 

\begin{enumerate}[(1)]
\item {\bf The quality of slide material:} How well does the presentation reveal its topic 
(at a level that is appropriate for your audience); quality of text editing, visual impression. 
\item {\bf The quality of the presentation event:} Was the speaker competent to speak about the subject, 
was the presentation engaging and thought provoking?
\item {\bf Meeting the objectives:} Did the exercises, questions or demos help to acquire skills.
How well did the presenter motivate you to learn some new skills, conceptual knowledge. 
Were the exercises/demos carefully selected? Were the objectives and 
summaries/take-aways clearly stated during the presentation?
\item {\bf Overall impression:} Would you suggest to your friends or any other people 
(such as mathematically inclined students in BBA; your brothers and sisters etc.) 
to attend this presentation by this presenter \textendash{} is it worth their time?
\end{enumerate}


Here is the suggested sequence of steps:

\begin{enumerate}[(A)]
\item By {\bf March 24, 2020} every presenter submits $4$ suggested questions about his/her topic. 
See ``Guidelines: Part 3'' to see the available questions. 
These something that you feel people should know AFTER they have listened to your presentation. 
\item By {\bf March 24, 2020} every presenter submits the finalized presentation.
\item Until {\bf March 27, 2020} instructor reviews the submitted questions and presentations; 
and whenever the presentation is ready, schedules the delivery date.
\item Instructor also creates a quiz with about $18$ questions (one question per each presentation; 
it may be identical to one of the $4$ questions you submitted or a simple variant, e.g.\ 
some numbers may be replaced or minor editing changes, etc.).
\item Every participant delivers his/her individual presentation. 
{\bf At the same time} everybody fills the evaluation for the presenter plus short feedback (in a spreadsheet I will provide).
Please do not delay this, since you will forget your impressions.
\item {\bf Early April:} All the presentations are done and we all take the quiz (based on your questions, 
but the final version of it is edited by the instructor). 
\item Just after taking the quiz, you submit your evaluations for all the other participants.
\item Instructor grades the quiz and distributes the grades for presentations (the mean grade corresponds
to the mean grade for the quiz; but individual grades will be higher for those participants who got better 
evaluations). 
\item Everybody gets (anonymized) evaluations of others and also their feedback; what did your colleagues
think about your slidedeck, presentation event, how precisely the objectives were met, what is the overall impression. 
\end{enumerate}

{\em Note 1.} Your grade will be based only upon the evaluations of your presentation
(see criteria (1),(2),(3),(4) above). We do not take into account, how students have answered YOUR question in the quiz.
It is possible to ask a challenging quiz question, and still give a good and meaningful presentation
(and also vice versa - asking easy quiz questions does not guard you against the risks of delivering 
a presentation that the audience does not particularly enjoy.)

{\em Note 2.} Instructor tries to ensure that the quiz contains interesting (but not unnecessarily difficult) questions.
We expect that everybody will suggest some interesting questions about your topic; 
and that your colleagues will mostly be able to answer them (if they have carefully listened to the presentation). 
 

\end{document}



