%%
%% This is file `./samples/shortsample.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% apa6.dtx  (with options: `shortsample')
%% ----------------------------------------------------------------------
%% 
%% apa6 - A LaTeX class for formatting documents in compliance with the
%% American Psychological Association's Publication Manual, 6th edition
%% 
%% Copyright (C) 2011-2017 by Brian D. Beitzel <brian at beitzel.com>
%% 
%% This work may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License (LPPL), either
%% version 1.3c of this license or (at your option) any later
%% version.  The latest version of this license is in the file:
%% 
%% http://www.latex-project.org/lppl.txt
%% 
%% Users may freely modify these files without permission, as long as the
%% copyright line and this statement are maintained intact.
%% 
%% This work is not endorsed by, affiliated with, or probably even known
%% by, the American Psychological Association.
%% 
%% ----------------------------------------------------------------------
%% 
\documentclass[jou]{apa6}

\usepackage[american]{babel}

\usepackage{csquotes}
\usepackage[style=apa,sortcites=true,sorting=nyt,backend=biber]{biblatex}
\DeclareLanguageMapping{american}{american-apa}
\addbibresource{bibliography.bib}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Discrete Structures
%% The start of RBS stuff
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Working internal and external links in PDF
\usepackage{hyperref}
% Extra math symbols in LaTeX
\usepackage{amsmath}
\usepackage{gensymb}
\usepackage{amssymb}
% Enumerations with (a), (b), etc.
\usepackage{enumerate}
\usepackage{fancyvrb}
\usepackage{xcolor}

\let\OLDitemize\itemize
\renewcommand\itemize{\OLDitemize\addtolength{\itemsep}{-6pt}}

\usepackage{etoolbox}
\makeatletter
\preto{\@verbatim}{\topsep=3pt \partopsep=3pt }
\makeatother

% These sizes redefine APA for A4 paper size
\oddsidemargin 0.0in
\evensidemargin 0.0in
\textwidth 6.27in
\headheight 1.0in
\topmargin -24pt
\headheight 12pt
\headsep 12pt
\textheight 9.19in

\setlength\parindent{0pt}

\title{Quiz for Week02}
\author{Discrete Structures, Fall 2020}
\affiliation{RBS}

\leftheader{Discrete Structures Lab03: Hints}

\abstract{%
}

%\keywords{}

\begin{document}
%\maketitle

%\twocolumn
{\Large Lab03/Lab04: Hints}

\thispagestyle{empty}

\section{How to set up your environment}

Check out from Git the template project.\\
Step-by-step instructions not available yet.

\section{Testing procedure}

Perform these steps, to see what grade you would get.

\begin{enumerate}
\item Open a terminal window in any empty directory. Get code from your repository:
\begin{verbatim}
git clone <repository-url>
\end{verbatim}
\item Add two lines to the {\tt build.sbt} file \textendash{} to enable HTML report generation 
(follow the link, if you need to see the whole SBT buildfile). 
{\footnotesize
\begin{verbatim}
libraryDependencies += "com.vladsch.flexmark" % "flexmark-all" % "0.35.10"
testOptions in Test += Tests.Argument(TestFrameworks.ScalaTest, "-h", "target/test-reports")
\end{verbatim}
}
\item Copy the testfiles {\tt KMPtheprivateTest.scala} and {\tt BMtheprivateTest.scala} under your 
\begin{verbatim}
$ProjectRoot/src/test/scala/lv/rbs/ds/lab03/ 
\end{verbatim}
\item Run from the commandline: 
\begin{verbatim}
sbt
testOnly *theprivateTest
\end{verbatim}
\item After this the test reports as HTML are visible under subdirectory {\tt target}.
\end{enumerate}



\section{Some things to avoid}

In short, follow all the naming conventions carefully.

\begin{enumerate}[(1)]
\item {\bf Wrong package names.}\\
Instead of  "lv.rbs.ds.lab03" do not rename it into 
"lv.rbs.ds.lab04", or "scala.lv.rbs.ds.lab03", or "main.scala.lv.rbs.ds.lab03". 
\item {\bf Wrong directory structure.}
If your IDE (such as IntelliJ Idea) 
complains, find a way to set up your project so that it matches the Maven/SBT directory layout.
Broken Maven directory structure - the classfiles located outside /src/main/scala... directory.
\item {\bf Wrong class names}\\
Do not use "BoyerMoore.scala" instead of "BMmatcher.scala" etc. It breaks all the tests.
\item {\bf Wrong function names}\\
Do not use {\tt "get\textunderscore{}Json(...)"} or anything strange instead of {\tt toJson(...)}. 
\item Verify that you return right value type. (If it is a list, it should be the right kind of list; and it should 
contain the right kind of tuples.)
\item {\bf JSON files generated in ad-hoc ways.} Handmade JSON may contain broken key names with extra spaces, and other syntax that renders 
them unusable.
\end{enumerate}




\end{document}






