%%
%% This is file `./samples/shortsample.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% apa6.dtx  (with options: `shortsample')
%% ----------------------------------------------------------------------
%% 
%% apa6 - A LaTeX class for formatting documents in compliance with the
%% American Psychological Association's Publication Manual, 6th edition
%% 
%% Copyright (C) 2011-2017 by Brian D. Beitzel <brian at beitzel.com>
%% 
%% This work may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License (LPPL), either
%% version 1.3c of this license or (at your option) any later
%% version.  The latest version of this license is in the file:
%% 
%% http://www.latex-project.org/lppl.txt
%% 
%% Users may freely modify these files without permission, as long as the
%% copyright line and this statement are maintained intact.
%% 
%% This work is not endorsed by, affiliated with, or probably even known
%% by, the American Psychological Association.
%% 
%% ----------------------------------------------------------------------
%% 
\documentclass[jou]{apa6}

\usepackage[american]{babel}

\usepackage{csquotes}
\usepackage[style=apa,sortcites=true,sorting=nyt,backend=biber]{biblatex}
\DeclareLanguageMapping{american}{american-apa}
\addbibresource{bibliography.bib}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Discrete Structures
%% The start of RBS stuff
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Working internal and external links in PDF
\usepackage{hyperref}
% Extra math symbols in LaTeX
\usepackage{amsmath}
\usepackage{gensymb}
\usepackage{amssymb}
% Enumerations with (a), (b), etc.
\usepackage{enumerate}

\let\OLDitemize\itemize
\renewcommand\itemize{\OLDitemize\addtolength{\itemsep}{-6pt}}

\usepackage{etoolbox}
\makeatletter
\preto{\@verbatim}{\topsep=3pt \partopsep=3pt }
\makeatother

% These sizes redefine APA for A4 paper size
\oddsidemargin 0.0in
\evensidemargin 0.0in
\textwidth 6.27in
\headheight 1.0in
\topmargin -24pt
\headheight 12pt
\headsep 12pt
\textheight 9.19in



\title{Discrete Structures (W1): Sample Quiz}
\author{Kalvis}
\affiliation{RBS}

\leftheader{Discrete Structures (W1)}

\abstract{These are sample questions \textendash{} they are similar, but not identical 
to the actual quiz planned for January 16, 2020. 
The actual quiz will have $7$ questions, its time is $15$ minutes; 
it accounts for 7~\textperthousand{} of your total grade.
% 7*8 + 11*4
}

%\keywords{}

\begin{document}
\maketitle

{\bf Question 1.} Let $a,b \in \mathbb{Z}^{+}$ be two positive integers.
Use quantifiers to write
a statement that $d$ is the greatest common divisor of $a,b$ (that is, 
the greatest number that divides both $a$ and $b$). For example $\mbox{g\\
{\em Note.} Use ``infix'' notation for common predicates: write 
$a\,\mid\,b$ whenever $a$ divides $b$; write $x < y$, if $x$ is less than $y$.\\
For example $3\,|\,6$ ($3$ divides $6$) is preferred compared to 
``$\mathtt{divides}(3,6)$''. Also $10 < 17$ is more readable than
``$\mathtt{lessThan(10,17)}$''.

\vspace{10pt}
{\bf Question 2.} Use quantifiers to write a statement to tell that a quadratic
function $f(x) = ax^2 +bx+c$ has two different integer roots.


\vspace{10pt}
{\bf Question 3.} Assume that for some argument {\tt x}, 
Python functions {\tt a(x)} and {\tt b(x)}
return value {\tt True}, but other two functions 
{\tt c(x)} and {\tt d(x)} return value {\tt False}. 
Which functions are called and evaluated, if you run the following conditional statement:
\begin{verbatim}
if (a(x) or b(x)) and (c(x) \& d(x)):
    ...
\end{verbatim}
{\em Note.} Note that Boolean operators {\tt and}, {\tt or} use {\em short-circuit
evaluation}, but operators {\tt \&}, {\tt |} do not. 


\vspace{10pt}
{\bf Question 4.} There is a set $C$ of several children and a 
set $H$ of several hats. There is a predicate $W(c,h)$ which is {\tt True}
iff the child $c \in C$ has ever worn the hat $h \in H$.\\
{\bf (a)} Write the domain set and the range set of the predicate function $W$. \\
{\bf (b)} Use quantifiers to write a statement: ``Every two different children 
have at least one hat that they have both worn.''


\vspace{10pt}
{\bf Question 5.}
Let $\mathcal{H}$ be the set of all humans, and the predicate $F(x,y)$ is
true iff $x$ is the father of $y$. Express these sentences in plain English:
{\bf (a)} $\forall x \in \mathcal{H}\;\exists y \in \mathcal{H},\;F(x,y)$.
{\bf (b)} $\exists y \in \mathcal{H}\;\forall x \in \mathcal{H},\;F(x,y)$. 
{\bf (c)} Which of the two statements {\bf (a)}, {\bf (b)} (if any) 
is true, if we replace the non-empty domain of all humans $\mathcal{H}$ by an
empty domain $\mathcal{Z} = \emptyset$ of all zombies?

Truth tables for 3-valued domain (and 2-argument predicate). 



\newpage 

\section{Answers}


{\bf Question 1:} Answer:

\begin{tabular}{ c | c | c | c }
$p$ & $q$ & $r$ & ? \\ \hline
{\tt T} & {\tt T} & {\tt T} & {\tt T} \\ \hline
{\tt T} & {\tt T} & {\tt F} & $\boxed{\mathtt{T}}$ \\ \hline
{\tt T} & {\tt F} & {\tt T} & {\tt F} \\ \hline
{\tt T} & {\tt F} & {\tt F} & $\boxed{\mathtt{T}}$ \\ \hline
{\tt F} & {\tt T} & {\tt T} & {\tt T} \\ \hline
{\tt F} & {\tt T} & {\tt F} & $\boxed{\mathtt{F}}$ \\ \hline
{\tt F} & {\tt F} & {\tt T} & {\tt F} \\ \hline
{\tt F} & {\tt F} & {\tt F} & $\boxed{\mathtt{F}}$ \\ \hline
\end{tabular}

\vspace{3pt}
\noindent
Note that $r=\mathtt{false}$ in all the unknown slots. 
We can simplify the Boolean expression:
\begin{align}
E & \equiv \neg(r \rightarrow \neg q) \vee (p \wedge \neg r) \equiv \nonumber \\
  & \equiv \neg(\mathtt{false} \rightarrow \neg q) \vee 
(p \wedge \mathtt{true}) \equiv  \nonumber \\
  & \equiv \neg(\mathtt{true}) \vee p \equiv \nonumber \\
  & \equiv \mathtt{false} \vee p \equiv p. \nonumber
\end{align}
Therefore we simply copy the value of $p$ in all four places.

\vspace{10pt}
{\bf Question 2:} Answer: {\bf (C)}.\\
The truth table is identical to $p \oplus q$ (exclusive OR). 
To see that answer {\bf (C)} is correct, apply De Morgan's law multiple times:
\begin{align}
\neg (\neg ( p \wedge \neg q) \wedge \neg (\neg p \wedge q)) & \equiv \nonumber \\
\neg \neg (p \wedge \neg q) \vee \neg \neg (\neg p \wedge q) & \equiv \nonumber \\
(p \wedge \neg q) \vee (\neg p \wedge q). & \nonumber
\end{align}

The last expression is exactly the exclusive OR (either $p$ is {\tt true} and
$q$ is {\tt false} or vice versa).

\vspace{10pt}
{\bf Question 3:} Answer: Yes,
$(\neg p \vee \neg q) \wedge (p \rightarrow q)$ is 
satisfiable.\\
Subexpression $(\neg p \vee \neg q)$ tells that either $p$ 
or $q$ (or both) should be {\tt false}. So, you should take
$p = \mathtt{false}$ to make $p \rightarrow q$ {\tt true} as well. 


\vspace{10pt}
{\bf Question 4.} Answer: $\neg A \rightarrow \neg B$ (or $B \rightarrow A$).\\
Condition $C$ is called {\em sufficient} for the result $R$, if 
$R$ is {\tt true} whenever $C$ is {\tt true}. 
This means that {\bf not} eating vegetables logically implies {\bf not} 
getting ice cream. It is exactly $\neg A \rightarrow \neg B$.\\
You can rewrite it as a contrapositive, if you like: $B \rightarrow A$:
getting ice cream implies having eaten vegetables. Both answers are
equivalent.

\vspace{10pt}
{\bf Question 5.} Answer: Yes, $E_1$ and $E_2$ are logically equivalent 
(they mean the same thing).
Consequently, there is no way to assign $p,q,r$ to make their truth values different.

\begin{itemize}
\item $p \rightarrow (\neg q \wedge r)$ means that either condition ($p$) is {\tt false} or 
the conclusion ($\neg q \wedge r$) is {\tt true}. So, $E_1$ can be rewritten as 
$\neg p \vee (\neg q \wedge r)$.
\item In $E_2$ the subexpression 
$\neg(r \rightarrow q)$ can be rewritten as $(r \wedge \neg q)$
(for the implication $r \rightarrow q$ to be {\tt false}, you should have
both $r = \mathtt{true}$ and $q = \mathtt{false}$, so it 
means $(r \wedge \neg q)$. And that is exactly the same expression we got 
from $E_1$, since $(r \wedge \neg q) = (\neg q \wedge r)$
\end{itemize}



\vspace{10pt}
{\bf Question 6.} Answer: $(r \wedge h) \rightarrow t$\\
"Only if" means {\bf necessity}. Namely, $(r \wedge h)$ implies $t$, 
or $(r \wedge h) \rightarrow t$ (Ability to use a high occupancy road during a rush 
hour implies at least three people in the car.)\\
You can rewrite this as a contrapositive (and expand $(r \wedge h)$ 
with De Morgan's law). Say, "If you do not have three people
in your car, then it is either not a high occupancy road, or it is not a rush hour."
This is an equivalent statement $\neg t \rightarrow (\neg r \vee \neg h)$. 


\vspace{10pt}
{\bf Question 7a.} Answer: $A$ is a knave; $B$ is a knight.\\
We sort cases.\\
(1) Assume that $A$ is a knight. He says that $B$ is a knave (and that must be true, 
since $A$ does not lie). 
But then $B$ should lie, when he says "At least one of us is a knight". 
The opposite of "At least one" ($\geq 1$) is "less than one" ($<1$); so in this
case there should be no knights at all. This is a contradiction. Therefore $A$ cannot be a knight.\\
(2) Assume that $A$ is a knave. Since he says that $B$ is a knave, $B$ should be a knight. 
And moreover, since $B$ says that "at least one of us is a knight", then 
it is still consistent, because he is a knight himself. 

\vspace{10pt}
{\bf Question 7b.} TBD (I can explain this in the class, if you wish.)



\end{document}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% End of RBS stuff
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%% 
%% Copyright (C) 2011-2017 by Brian D. Beitzel <brian at beitzel.com>
%% 
%% This work may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License (LPPL), either
%% version 1.3c of this license or (at your option) any later
%% version.  The latest version of this license is in the file:
%% 
%% http://www.latex-project.org/lppl.txt
%% 
%% Users may freely modify these files without permission, as long as the
%% copyright line and this statement are maintained intact.
%% 
%% This work is not endorsed by, affiliated with, or probably even known
%% by, the American Psychological Association.
%% 
%% 
%% This work is "maintained" (as per LPPL maintenance status) by
%% Brian D. Beitzel.
%% 
%% This work consists of the file  apa6.dtx
%% and the derived files           apa6.ins,
%%                                 apa6.cls,
%%                                 apa6.pdf,
%%                                 README,
%%                                 APAamerican.txt,
%%                                 APAbritish.txt,
%%                                 APAdutch.txt,
%%                                 APAenglish.txt,
%%                                 APAgerman.txt,
%%                                 APAngerman.txt,
%%                                 APAgreek.txt,
%%                                 APAczech.txt,
%%                                 APAturkish.txt,
%%                                 APAendfloat.cfg,
%%                                 apa6.ptex,
%%                                 TeX2WordForapa6.bas,
%%                                 Figure1.pdf,
%%                                 shortsample.tex,
%%                                 longsample.tex, and
%%                                 bibliography.bib.
%% 
%%
%% End of file `./samples/shortsample.tex'.
